Statistical Modeling of Galaxy Catalogues with Normalizing Flows

### 2022-05-27 src/tex/ms.tex
All main and conditional flow scripts now exist.

\begin{figure*}[t!]
    \script{plot_main_galaxy_corner.py}
    \begin{centering}
        \includegraphics{figures/main_galaxy_corner.pdf}
        \caption{
            Distribution of the CosmoDC2 test set compared to the distribution learned by PZFlow.
            The close overlap of every pair-wise disttribution demonstrates that PZFlow was able to learn the structure present in CosmoDC2 with high fidelity.
        }
        \label{fig:main-corner}
    \end{centering}
\end{figure*}

@@

@@

\appendix
A. Failed (?) experiments

@@

B. LSST Error Model

C. Benchmarking PZFlow

>>>>

\begin{figure*}[t!]
    \script{plot_main_galaxy_corner.py}
    \begin{centering}
        \includegraphics{figures/main_galaxy_corner.pdf}
        \caption{
            Distribution of the CosmoDC2 test set compared to the distribution learned by PZFlow.
            The close overlap of every pair-wise distribution demonstrates that PZFlow was able to learn the structure present in CosmoDC2 with high fidelity.
        }
        \label{fig:main-corner}
    \end{centering}
\end{figure*}

@@

\begin{figure*}[t!]
    \script{plot_conditional_galaxy_corner.py}
    \begin{centering}
        \includegraphics{figures/conditional_galaxy_corner.pdf}
        \caption{
            Distribution of the ellipticities and sizes of the galaxies in the CosmoDC2 test set compared to the distribution learned by PZFlow.
            The close overlap of every pair-wise distribution demonstrates that PZFlow was able to learn the structure present in CosmoDC2 with high fidelity.
        }
        \label{fig:conditional-corner}
    \end{centering}
\end{figure*}

@@

\appendix

\section{Training details}

\begin{figure*}[t!]
    \script{plot_galaxy_flow_losses.py}
    \begin{centering}
        \includegraphics{figures/galaxy_flow_losses.pdf}
        \caption{
            Training losses for the galaxy flows.
        }
        \label{fig:galaxy-flow-losses}
    \end{centering}
\end{figure*}

\section{LSST Error Model}

\section{Failed experiments}

@@

\section{Benchmarking PZFlow}
